### 2019-01-26 thesis_report/results.tex
Fixed small mistake making latex crash

			\begin{figure}[!htb]
			\centering
			\includegraphics[width=0.55\columnwidth]{figures/wavefunctions}
			\caption{Wavefunctions for different sizes and geometries.
			With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinosoid, and (d) a system with vertically offset sinosoids.
			Inside the figure we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
			We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap}$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
			\label{fig:wavefunctions}}
			\end{figure}

			\comment{We calculate the lowest eigenfunction and plot the density.}
			Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
			In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
			Also displayed in the figure are the energies $\E_M$, corresponding to the plotted Majorana wavefunctions, as well as $E_1$: the energies corresponding to the next lowest state.

>>>>

			\begin{figure}[!htb]
			\centering
			\includegraphics[width=0.55\columnwidth]{figures/wavefunctions}
			\caption{Wavefunctions for different sizes and geometries.
			With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinosoid, and (d) a system with vertically offset sinosoids.
			Inside the figure we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}$.
			We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
			\label{fig:wavefunctions}}
			\end{figure}

			\comment{We calculate the lowest eigenfunction and plot the density.}
			Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
			In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
			Also displayed in the figure are the energies $E_M$, corresponding to the plotted Majorana wavefunctions, as well as $E_1$: the energies corresponding to the next lowest state.
